\documentclass{report}
\usepackage{homework}
\solstrue

\renewcommand{\hmwkTitle}{Homework 2}

\begin{document}
\mktitle

\begin{problem}

\newcommand{\ENDL}{$<$CR$>$$<$LF$>$}

Consider the following string of ASCII characters that were captured by $Wireshark$ when the browser sent an HTTP GET message (i.e., this is the actual content of an HTTP GET message). The characters \texttt{\ENDL{}} are carriage-return and line-feed characters. Answer the following questions, indicating where in the HTTP GET message below you find the answer.\\

\begin{raggedright}
\texttt{GET /classes/spring17/cs118/project-1.html HTTP/1.1\ENDL\\
Host: web.cs.ucla.edu\ENDL\\
Connection: keep-alive\ENDL\\
Upgrade-Insecure-Requests: 1\ENDL\\
User-Agent: Mozilla/5.0 (Macintosh; Intel Mac OS X 10\_12\_3) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/56.0.2924.87 Safari/537.36\ENDL\\
Accept: text/html,application/xhtml+xml,application/xml;q=0.9,image/webp,*/*;q=0.8\ENDL\\
Referer: http://web.cs.ucla.edu/classes/spring17/cs118/homeworks.html\ENDL\\
Accept-Encoding: gzip, deflate, sdch\ENDL\\
Accept-Language: en-US,en;q=0.8,lv;q=0.6,ru;q=0.4\ENDL\\
If-None-Match: "5a17-54c4847c4f640-gzip"\ENDL\\
If-Modified-Since: Mon, 03 Apr 2017 19:36:49 GMT\ENDL\\
}
\end{raggedright}

\begin{enumerate}
\item What is the \textbf{full} URL of the document requested by the browser?
\item What version of HTTP is the browser running?
\item What type of browser initiates this message? Why is the browser type needed in an HTTP  request message?
\item Can you find the IP Address of the host on which the browser is running from the captured HTTP request?
\end{enumerate}

\begin{answer}{30em}
    Write your answer here
\end{answer}

\end{problem}


\newpage



\begin{problem}
For each of the questions below, describe answer in terms of low-level packet sequences, drops, or network-level packet reordering.

\begin{enumerate}
  
\item A specific case where HTTP/1.1 wins in performance compared to HTTP/1.0

\item A specific case where HTTP with web caching wins in performance compared to HTTP without caching

\end{enumerate}

\begin{answer}{30em}
    Write your answer here
\end{answer}

\end{problem}

\newpage




\begin{problem}
Suppose within your Web browser you click on a link to obtain a Web page. The IP address for the associated  URL is cached in your local host, so a DNS look-up is not needed. Suppose that the Web page associated with the link is a small HTML file, consisting only of references to 100 very small objects on the same server. Let $RTT_0$ denote the RTT between the local host and the server containing the object. How much time elapses (in terms of $RTT_0$) from when you click on the link until your host receives all of the objects, if you are using:
\begin{enumerate}
		\item HTTP/1.0 without parallel TCP connections?
		\item HTTP/1.0 with parallel TCP connections?
		\item HTTP/1.1 without parallel connections, but with pipelining?
\end{enumerate}

Ignore any processing, transmission, or queuing delays in your calculation.\\

  \begin{answer}{37em}
  Write your answer here
  \end{answer}

\end{problem}

\newpage


\begin{problem}
BitTorrent is a communication protocol for peer-to-peer file sharing which is used to distribute data (or files) over the Internet.
	\begin{enumerate}
		
		\item Consider a new peer A that joins BitTorrent swarm without possessing any chunks. Since peer A has nothing to upload, peer A cannot become a top uploader for any of the other peers. How then will peer A get the first chunk?
		
		\item Explain why BitTorrent is primarily useful for popular files but not for unpopular files.
		
		\item Consider two DHTs (Distributed Hash Table) with a mesh overlay topology and a circular overlay topology, respectively. What are the advantages and disadvantages of each design?
		
	\end{enumerate}

  \begin{answer}{35em}
  Write your answer here
  \end{answer}

\end{problem}

\newpage



\begin{problem}
The server tries to distribute a file of $F=15Gbits$ to $N$ clients (peers). The server has an upload rate of $u_{s}=30Mbps$, and each peer has a download rate of $d_{p}=2Mbps$ and upload rate of $u_{p}=1Mbps$. How long does it take to distribute if there are 1,000 peers for both \textbf{client-server distribution} and \textbf{P2P distribution}. \\

  \begin{answer}{35em}
  Write your answer here
  \end{answer}

\end{problem}




\end{document}
